\documentclass[11pt,twocolumn]{article}
\usepackage[margin=0.8in]{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage[breaklinks=true, colorlinks=true, linkcolor=red, urlcolor=blue, citecolor=black]{hyperref}
\urlstyle{rm}
\usepackage{mathptmx}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{color}
\usepackage{sidecap}
\usepackage{authblk}
\usepackage{booktabs}
\usepackage[font=small,labelfont=bf]{caption}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\def\bfr{\bf\color{red}}
\def\geohub{{\tt geohub}}
\def\Count{count}
\def\ntracts{39}
\def\nprof{8}
\def\nvol{31}

\title{\bf
	Results of the 2021 Volunteer Greater Hollywood Homeless Count
	}
\author[*,$\dagger$,$\ddagger$]{Louis Abramson, PhD}%,$\ddagger$
\affil[*]{\it Hollywood 4WRD Homelessness Coalition, 6255 Sunset Blvd, Ste 150, LA, CA 90028}
\affil[$\dagger$]{\it Central Hollywood Neighborhood Council, PO Box 93907, LA, CA 90093}
\affil[$\ddagger$]{\it Carnegie Observatories, 813 Santa Barbara St, Pasadena, CA 91101}
\affil[ ]{\href{mailto:labramson.chnc@gmail.com}{labramson.chnc@gmail.com}}
%\affil[$\dagger$]{\it Princeton University, 4 Ivy Lane, Princeton, NJ 08544}
%\href{mailto:labramson.chnc@gmail.com}{labramson.chnc@gmail.com}}

\date{\today}                                           % Activate to display a given date or no date

\begin{document}
\maketitle

\begin{abstract}

\end{abstract}

\section{Introduction}
\label{sec:intro}

The Los Angeles Homelessness Services Authority (LAHSA) has conducted an annual Point In Time PIT) 
census of the unhoused population of Los Angeles County every year since 20{\bfr XX}. These data are critical to 
essentially all homelessness-related activities in the County and its municipalities. They inform programmatic
funding levels, educate residents, undergird local and state legislative efforts, and shape the day-to-day 
practices of thousands of professional and volunteer service providers. As the official assessment of the 
scope of one of the most pressing humanitarian issues of our time, the LAHSA Count is therefore invaluable.

Disruptions from COVID-19 have only further emphasized the need for such data. As incomes fluctuated,
many of Los Angeles' already sizable number of housing-unstable residents may have been pushed off
couches or out of apartments and onto the street. As such, while the epidemiological considerations of 
conducting an all-volunteer, countywide census are real, the damage from failing to do so is also substantial.

Given the non-uniformity in volunteerism and resources across LAHSA's large area of operations, 
the challenges of COVID were ultimately deemed sufficient to cancel the formal 2021 PIT census of 
unsheltered Angelenos. However, not all communities agreed with this decision, and many had the resources
to execute a robust---if unsponsored---survey on their own. Hollywood is one such community.

Greater Hollywood is an epicenter of LA's homelessness crisis. According to the official 2020 
Count, the Hollywood and East Hollywood Continua of Care (CoC) were home to 2203 unhoused residents,
1714 of whom (78\%) were living unsheltered on the street. This figure corresponds to roughly 5\% of LA's 
homeless population concentrated in an area with only 2.5\% ({\bfr CITE}) of its total population. In some 
regions within those CoCs, fully 1-in-30 residents are unhoused compared to 1-in-100 citywide.

While the above statistics are tragic, Hollywood is also marked by its community of professional
and volunteer service providers, solutions-minded residents and businesspeople, and attuned political 
leaders. Increasingly formal coalitions of the above stakeholders are spreading across the district, dedicated 
to humanely ending the homelessness crisis. All of them rely on the annual PIT count for educational, 
financial, and programmatic purposes. When communicating with the public, the starting point for 
many conversations is simply stating the size of the challenge. When communicating with funders, it is 
similarly critical to convey how many people require services. When designing legislation---especially given 
the shock of COVID-19 and in the face of looming court proceedings---knowing how many unhoused 
Angelenos live where is foundational. For these reasons, organizations and individuals in Hollywood 
decided to with a 2021 Homeless \Count irrespective of other governmental decisions.

This document describes the methodology and findings of that \Count, conducted on the night of 
Thursday, February 25. Below, Section \ref{sec:procedure} describes the volunteer data acquisition, 
analysis, and training protocols. Section \ref{sec:results} present estimates of the unsheltered 
population in the Hollywood, East Hollywood, and Greater Hollywood CoCs. Section \ref{sec:discussion}
contextualizes those findings in terms of previous LAHSA results and describes factors that would
modulate them upwards or downwards. Section \ref{sec:summary} summarizes. Additional information
can be found in the Appendix, including a table of tract-level results in each of the survey's 39 US 
Census tracts.

\section{Methodology}
\label{sec:procedure}

Our \Count\ adhered as closely as possible to the official LHASA 2020 PIT data collection and 
analysis protocols. The event took place on 25 February 2021 beginning at 7.00 PM. This date and time
correspond to roughly one month after and four hours earlier than the official event would have occurred. 
Ancillary data in other census tracts suggests that the date offset is unlikely to substantially erode 
comparability between this and past datasets, though {\bfr what can we say about time of day effects}.

The \Count\ was based out of {\it The Center at Blessed Sacrament} (``The Center''), a major service 
provider in Hollywood. All volunteer teams launched from and returned to this location as they would 
in previous years to a LHASA community counting hub. The major difference was that training was 
performed remotely as a COVID precaution.

\subsection{Data Acquisition}
\label{sec:acquisition}

The \Count\ covered the \ntracts\ US Census tracts constituting the LAHSA-defined Hollywood 
and East Hollywood Continua of Care (CoC). As such, our results are integrable at the tract, CoC, 
and Greater Hollywood community levels. The Appendix presents tract-level tallies and raw
individual/dwelling counts while the main text discusses CoC-level results. Greater Hollywood 
results are available but not directly comparable to any official service geography and therefore
serve a descriptive purpose only.

All tracts were vetted by professionals from {\it The Center} prior to assignment. Tracts deemed 
especially challenging---e.g., due to their proximity to freeway onramps and peripheries---were 
reserved for professional counting teams. Vetting produced \nprof\ such tracts, which were surveyed 
by outreach personnel from {\it The Center} and {\it Covenant Hous} during daylight hours on 25 
February (circa {\bfr XXX PM}). The remaining \nvol\ tracts were divided among the volunteer 
car-based teams and surveyed beginning at 7.00 PM. Table \ref{tbl:tracts} records which kind of team 
surveyed each tract.

We recruited XXX teams of at least two people YYY of which participated in the \Count\ itself. We 
limited participation to existing``pods'' of two to three people---typically families---to ensure that the 
COVID status of each participant was controlled and the possibility of transmission minimized. 
Singlet volunteers were also admitted but remained on-site to assist with material distribution, 
collection, and data quality control processes. All participants wore proper personal protective 
equipment and maintained social distancing when appropriate.

Each car-based volunteer team comprised at least a Driver and a Counter and was assigned two tracts 
to count. Three-person teams also included a Navigator per 2020 LAHSA PIT protocols. In such teams, 
the Navigator held the map and directed the Driver while the Counter tallied unhoused individuals/dwellings 
and the Driver drove. In two-person teams, the Counter doubled as the Navigator. Training emphasized 
driving techniques aimed at reducing the Counters' cognitive loads and so minimize counting errors. 
These included driving slowly using hazard lights and covering interior streets in a serpentine pattern 
before circling the tract border. Teams were instructed to count both sides of interior streets but only
interior sides of border streets.

Upon arriving at {\it The Center}, organizers gave each team a clipboard with:
\begin{enumerate}
	\item tract maps;
	\item tally sheets;
	\item a 1-page primer summarizing their training with a contact number for issues when deployed.
\end{enumerate}
Examples of each of the above documents are included in the Appendix.

The tally sheets were the most important data acquisition tool. They contained separate columns for
each of the nine categories of unhoused individuals or dwellings recognized in the 2020 LAHSA PIT
count: adults (ages $\geq$25),  transition age youths (18--24), unaccompanied minors, families 
(at least one adult with at least one minor), cars, vans, RVs, tents, and makeshift structures (CVRTM). 

All teams were deployed to their tracts by {\bfr XXX PM} and returned by {\bfr YYY PM}.

Upon returning, organizers approached each team with a tablet or laptop computer. Counters 
then verbally read-off their results for each category to the organizer, who entered the results into a 
google form/spreadsheet. Volunteer emails were also retained in case follow-up was necessry. The 
organizer read back the results for confirmation before recovering all materials---including hand-written 
tallies---from the volunteers.

Once all materials were collected, the organizers convened to cross-check the electronic records
with the physical tally sheets and identify any uncounted areas. {\bfr Follow-up teams were then 
dispatched to count the latter. This was necessary in only XXX instances.} 

{\bfr Given that the number of volunteer teams exceeded the number of tract assignments, a
subset of randomly selected tracts were chosen to be counted by multiple teams. Such duplicate 
measurements are useful for understanding random counting errors and are discussed in Sections 
\ref{sec:dupes} and \ref{sec:discussion}.}

\subsubsection{Volunteer Training}
\label{sec:training}

Teams underwent mandatory, approximately 30 minute Zoom-based training sessions before arriving 
for the \Count. Each participant was also required to watch the official 2020 LAHSA count training video 
and sign participation waivers.

The training covered the motivation for the \Count, an overview of the survey geography (the CoCs), 
the duties of the various team roles, and descriptions of the classes of unhoused individuals/dwellings,
including photographic examples of the latter. Volunteers were instructed to count dwellings and 
individuals separately and not to try to estimate how many people might live in or be associated with a 
specific dwelling. This ensured that final results could be analyzed as a function of CVRTM weights, 
which may change with future information (see Section \ref{sec:analysis}).

The only ``priming'' volunteers received pertained to the min/max estimate of tract-level 
individual+dwelling counts (``0--120'') and the likelihood of encountering unaccompanied minors or 
families (``very unlikely''). Both statements were informed by the official 2020 LAHSA PIT results
for the Greater Hollywood community. No other prior count-based information was established to 
minimize counter biases.

A recording of a volunteer training session is available at {\bfr WEBSITE}.

\subsection{Data Analysis}
\label{sec:analysis}

The core component of the raw data was a 9 column by $N_{\rm team}$ row spreadsheet containing the
tract-level tallies for each unhoused individual/dwelling class. The scheme of the analysis is simple:
\begin{enumerate}
	\item parse and associate tracts with CoCs;
	\item identify tracts counted by multiple teams;
	\item assess tract-level counting errors;
	\item upweight the CVRTM values by the 2020 LAHSA SPA4 CVRTM weights.
\end{enumerate}
The resultant $9\times39$ array can then be split and summed to provide CoC-level total counts, 
or breakdowns of the various classes of unhoused individuals dwellings. {\it These results will
correspond to the most likely values for the respective quantities in any geography.} However,
three uncertainties---one small and two large---complicate the interpretation of those sums. 
We discuss these in Section \ref{sec:discussion}, but account for them as best we can using 
Monte Carlo techniques to construct the full underlying probability distribution functions (PDFs) 
for each class in each tract.

All results discussed below derive from 10,000 Monte Carlo realizations of Item (5), above.


\subsubsection{Monte Carlo Estimations of Unhoused Probability Densities}
\label{sec:mc}

The point-in-time (PIT) data obtained by the Counters represent a draw from the underlying probability
distribution describing how many people are actually experiencing homelessness in a given tract. We have
only the PIT counts, but seek the actual number. We can estimate that as long as we have a model for
the intrinsic uncertainties in the PIT counts and demographic CVRTM weights. We have---or can 
model---both of these uncertainties, and can therefore reconstruct the full probability distribution 
functions (PDFs) using Monte Carlo sampling.

Here, Monte Carlo sampling is simply the process of randomly generating 10,000 alternate versions of
the PIT estimates that reflect what might happen if the count was conducted on a different day or by
a different counter. If you know how a quantity is expected to change from one measurement to another,
independien 

In all cases, baseline Poisson counting uncertainties exist in the raw counts. That is, if $n$ adults were 
Counted by one team in a given tract, the best guess is that the true number of unhoused adults 
in that tract falls between $n\pm\sqrt{n}$ about $2/3$ of the time. We therefore translate each raw 
count into 10,000 simulated counts where each entry refleby a Gaussian random number with standard deviation $\sqrt{n}$ 10,000
to all raw counts to simulate what we could expect to 

In the case of the CVRTM elements, these samplings incorporated both Poisson counting 
errors in the raw counts (random errors) and uncertainties in the CVRTM weights (systematic errors). 
In the case of the individual categories, only the Poison counting errors were propagated.

Explicitly, the $i$th estimate for the number of people in the $j$-th class of unsheltered person in any
tract is:

\begin{equation}\label{eq:monte}
	N_{i,j} = \left[n_{j} + \mathcal{N}(0,\sqrt{n_{j}})\right]\times\mathcal{N}(w_{j}, \sigma_{j})
\end{equation}
where $i$ runs form 1 to 10,1000, $n$ is the raw visual inspection result, $N(\mu,\Sigma)$ is a 
Gaussian random number with mean $\mu$ and standard deviation $\Sigma$, $w$ is the 2020 
LAHSA CVRTM weight for the appropriate class, and $\sigma$ is related to the standard error on that 
weight. For the individual classes---including families---$(w,\sigma)\equiv(1,0)$; i.e., weights were simply 
set to unity for all 10,000 trials.

Equation \ref{eq:monte} entails an assumption that the CVRTM weights, $w$, are normally distributed 
about their quoted values. If we had access to their full probability distribution of the CVRTM weights, we 
would not need to make this assumption. But, given that we did not have access to those distributions, $\sigma$
was calculated by assuming the quoted CVRTM weight was the maximum likelihood value, with a 95\%

The outcome is the equivalent of 10,000 $N_{\rm class}\times N_{\rm tract}$ arrays, each containing a different
point estimate for the size of the $i$th classes' population in the $j$th tract. Summing across trials thus
yields probability distributions that $N$ people of any class are dwelling in any tract.

{\bfr BASELINE BACKGROUND UNCERTAINTIES}

\subsection{Duplicate Measurements}
\label{sec:dupes}

\section{Results}
\label{sec:results}

\section{Discussion}
\label{sec:discussion}


\subsubsection{Null Entries}

The minor issue is null entries. As stated in Section \ref{sec:training}, some tracts may be 
relatively free of unhoused people. In these instances, many raw data will read ``0.'' This is
the best estimate of the relevant count in that geography at the time of inspection, but, due to 
Poisson noise, it is consistent with a range of small but non-zero values for the {\it true} count 
one might expect to find at any given time in that area. As such, null entries must be allowed 
to 

The spreadsheet of raw count data was downloaded from the internet before passing it through a number
of programs (written in IDL) to:


\section{Summary}
\label{sec:summary}

\appendix

\section{Example Documents}


\end{document}  